\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-09 fully-abstract-comp/popl2019/paper.tex

% How a program is lifted to an executable configuration
Given a program as defined in Definition~\ref{def:program-and-context}, we want to be able to execute it which means that we have to lift it to an executable configuration.
When we lift a program to an executable configuration, we need to provide it a stack in order for \stktokens{} to work.
The relation $(\comp_0, c_{\mathrm{main},c}, c_{\mathrm{main},d}) \rightsquigarrow \Phi$ lifts a component with a main to an executable configuration.
It works almost the same on \trgcm{} and \srccm{}.
On both machines a stack that contains all zeroes is added.
On \trgcm{} it is added as part of the memory along with the data and code memory.
On \srccm{} it is added as the free stack in the configuration, and the initial stack is empty as no calls have been made.
The component needs access to the stack, so a stack pointer is added to the register file in $\rstk$.
On \trgcm{} this is just a linear read-write capability, but on \srccm{} it is the representation of a stack pointer.
The entry point of the program is specified by main, so the two capabilities are unsealed (they must have the same seal) and placed in the $\pcreg$ and $\rdata$ registers.
The remainder of the registers contain zero.

>>>>

% How a program is lifted to an executable configuration
Given a program as defined in Definition~\ref{def:program-and-context}, we want to be able to execute it, meaning we have to lift it to an executable configuration.
When we lift a program to an executable configuration, we need to provide it a stack in order for \stktokens{} to work.
The relation $(\comp_0, c_{\mathrm{main},c}, c_{\mathrm{main},d}) \rightsquigarrow \Phi$ lifts a component with a main to an executable configuration.
It works almost the same on \trgcm{} and \srccm{}.
On both machines a stack that contains all zeroes is added.
On \trgcm{} it is added as part of the memory along with the data and code memory.
On \srccm{} it is added as the free stack in the configuration, and the initial stack is empty as no calls have been made.
The component needs access to the stack, so a stack pointer is added to the register file in $\rstk$.
On \trgcm{} this is just a linear read-write capability, but on \srccm{} it is the representation of a stack pointer.
The entry point of the program is specified by main, so the two capabilities are unsealed (they must have the same seal) and placed in the $\pcreg$ and $\rdata$ registers.
The remainder of the registers contain zero.
